### 2021-06-07 article/main.tex
Copy the proof in chap 3 into article

@@

\textbf {Proposition}
Let \m {\f} be given.
Then, for any random instance of \m {\f},
%
\Disp {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {2} {\pi} \log N 
}

\textbf {Proposition}
The bound
%
\Disp {
\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {3} L \RB {\log N_{H,t} + \log N_{H,r}} ^2
}
%
holds for probability \m {p}, with
%
\Disp {
1 -p
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}

@@

\textbf {Proposition}
It holds that
%
\Disp {
\Nm {\VNm {\M {F} _B \V {u}} _2 ^2 - 1}
\geq \d_s 
}
for probability \m {p}, with
\Disp {
1 -p
\leq 2 \mathsf {e} ^{-N_R \R {\d_s} /4} 
}

\textbf {Proposition}
Suppose
\Disp {
N_R
\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_{H,t}
}
Then \m {\M {F}_R} (respectively \m {\M {W} _R}) has \m {\d_s} RIP for probability \m {p}, with
\Disp {
1 -p
\leq \RB {\frac {\d_s} {N_{H,t} s}} ^{1/3} 
}

@@

The propositions below are taken from \cite {CaT07} and modified slightly in accordance to our settings, in addition to the generalization to complex vectors.
%
\textbf {Proposition}
{
\Disp {
\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
\leq \VNm {\V {d} _{\SB{\mathcal {A}}}} _1
+\VNm {\V {g} _{\SB{\mathcal {C}}}} _1 
}

@@

We discuss the complexity of DS, Lasso, and OMP.
Abbreviate \m {N_h = N_{H,t} N_{H,r}}.

For DS, suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used \cite {BoV04}.
For our case, that would be \m {\mathcal {O} \SB {4 N_h ^2 \D 8 N_h} = \mathcal {O} \SB {N_h ^3}}.

>>>>

Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity level \m {S} be fixed.
Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\mathcal {A}}}}, the largest-magnitude \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\mathcal {B}}}} the next \m {s} largest-magnitude components of \m {\V {g}}, and \m {\V {g} _{\SB{\mathcal {C}}}} are the components complement to \m {\V {g} _{\SB{\mathcal {A}}}}.
For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\mathcal {A}}} =\IP {0,0,-4,0,8}}, \m {\V {g} _{\SB{\mathcal {B}}} =\IP {0,3,0,2,0}}, and \m {\V {g} _{\SB{\mathcal {C}}} =\IP {-1,3,0,2,0}}.
In this section, the subscripts \m {\mathcal {A}, \mathcal {B}, \mathcal {C}} will bear analogous meaning.

We hope that \m {\VNm {\V {g} _{\SB{\mathcal {C}}}} _1} is small.
If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
We define, similarly, \m {\V {a} _{\SB{\mathcal {A}}}} and \m {\V {a} _{\SB{\mathcal {C}}}}, with sparsity level \m {s} different from \m {S}.
If \m {N} is large, we may forget for a moment that \m {s} is an integer.

@@

\textbf {Proposition 1}
Let \m {\f} be given.
Then, for any random instance of \m {\f},
%
\Disp {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {2} {\pi} \log N 
}

To show this, introduce
\Disp {
\psi \SB {\f, n_H}
:=\RB {
   \f \; \mathrm {Mod}\; \frac {2\pi} {N}
   + \RB {\frac {2 n_H} {N} + 1} \pi
} \;
\mathrm {mod}\; \RB {2\pi}
- \pi 
}
Also define
\Disp {
\Nm {D \SB {\psi'}}
:= &\frac {\Nm {\sin \SB {N \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \\
\leq &B \SB {\psi'}
:= \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \\
}
Then,
\Disp {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {N}
\VNm {
\RB {
   \sum_{n_H' =0}^{N -1}
      B \SB {\psi \SB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\mathcal {C}}}
} _1
}
Or, if we drop \m {s},
\Disp {
\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
\leq &\frac {1} {N} \D \frac {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \SB {\psi'} ^2 d \psi' \\
= &\frac {48} {N \pi^3}
\int _{s /N} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \\
\leq &\frac {2} {\pi} \log N 
}

\textbf {Proposition 2}
The bound
%
\Disp {
\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {3} L \RB {\log N_{H,t} + \log N_{H,r}} ^2
}
%
holds for probability \m {p}, with
%
\Disp {
1 -p
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}

@@

To investigate \m {\VNm {\M {F} _B \V {u}} _2} (respectively for \m {\M {W} _B}), we need a large deviation result for i.i.d.\ sum of chi-square random variables \cite {LaM00}, as below.

\textbf {Proposition 3}
It holds that
%
\Disp {
\Nm {\VNm {\M {F} _B \V {u}} _2 ^2 - 1}
\geq \d_s 
}
for probability \m {p}, with
\Disp {
1 -p
\leq 2 \mathsf {e} ^{-N_R \R {\d_s} /4} 
}

To investigate \m {\VNm {\M {F} _B \V {u}} _2} (respectively for \m {\M {W} _B}), we apply a bound for the failure probability of a DFT submatrix with \m {\d_s} RIP, in Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' \cite {KlM17}, and drop lower ordered terms as below,

\textbf {Proposition 4}
Suppose
\Disp {
N_R
\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_{H,t}
}
Then \m {\M {F}_R} (respectively \m {\M {W} _R}) has \m {\d_s} RIP for probability \m {p}, with
\Disp {
1 -p
\leq \RB {\frac {\d_s} {N_{H,t} s}} ^{1/3} 
}

Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {W}_B \M {W}_R} are \m {\d_s} RIP, it does appear (if we ignore the sparsity constraint) that \m {\M {P}} has approximately \m {2\d_s} RIP.
However, it remain to show that their Kronecker product still has RIP.

Nevertheless, notice that if angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}},
\Disp {
&\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \notag \\
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U} \D
   \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
   \M {U} ^\dagger \M {K} _t ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \D
   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} _t \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \notag \\
\eqsim &\VNm {\M {G}} _2 \RB {1 +2\d_s} 
}
Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}}.

@@

Set for short \m {\V {d} = \hat {\V {g}} - \V {g}}.
And for convenience, let \m {N_h = N_{H,t} N_{H,r}}.
%
To bound \m {\VNm {\V {d}} _2}, we illustrate that \m {\V {g}} can be seen as sparse, and for that purpose we generously bound \m {\d_{S}} by \m {1}.
We shall see below that it suffices to set
\Disp {
\g
= \R {2 \log N_h} 
}

The propositions below are taken from \cite {CaT07} and modified slightly according to our settings.

\textbf {Proposition 5}
\Disp {
\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
\leq \VNm {\V {d} _{\SB{\mathcal {A}}}} _1
+\VNm {\V {g} _{\SB{\mathcal {C}}}} _1 
}

\textbf {Proposition 6}
\Disp {
\VNm {\M {P}^\dagger \M {P} \V {d}} _\infty
\leq 2 \R {2 \log N_h} 
}
for probability \m {p}, with
\Disp {
1 -p
\leq N_h^{-1}.
}

\textbf {Proposition 7}
\Disp {
\VNm {\V {d}} _2
\leq \VNm {\V {d} _{\SB {\mathcal {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathcal {C}}}} _1 
}

\textbf {Proposition 8}
\Disp {
\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
\leq \frac {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\mathcal {AB}}}^\intercal P d} _2
+ \frac {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\mathcal {C}}}} _1 
}

Finally, we shall show the proposed bound.
For simplicity, set \m {S = Ls^2}, thus \m {S =L \log N_h}.
And, for concreteness, suppose \m {\d_S \leq \frac {1} {8}}.

\textbf {Theorem 9}
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then it holds that
\Disp {
\VNm {\V {d}} _2
\eqsim \mathcal {O} \SB {\R {L} \R {\log N_h}^3} 
}
for probability \m {p}, with
\Disp {
1 -p
\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_B /12}} 
}

To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by Proposition 6,
\Disp {
\VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \notag \\
\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \notag \\
\leq &2.83 \R {L} \log N_h
}
By \m {\ell_p}-norm inequality, by the definition of truncation, by Proposition 8, and by above,
\Disp {
\VNm {\V {d} _{\SB{\mathcal {A}}}} _1
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \notag \\
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \notag \\
\leq &3.44 L \R {\log N_h}^3
+0.262 \VNm {\V {d} _{\SB{\mathcal {C}}}} _1
}
Then, substituting this and Proposition 2 above into Proposition 5, we get
\Disp {
\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
\leq 5.12 L \RB {\log N_h}^2
}
Now Proposition 8 becomes
\Disp {
\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
\leq 3.44 \R {L} \log N_h + 1.35 \R {L} \R {\log N_h} ^3
}
Finally, by plugging \m {\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2} and \m {\VNm {\V {d} _{\SB{\mathcal {C}}}} _1} into Proposition 7, we get
\Disp {
\VNm {\V {d}} _2
\leq 4.79 \R {L} \R {\log N_h}^3
}
Therefore, we set \m {\chi = \R {L} \R {\log N_h}^3}, so that \m {\VNm {\V {d}} _2 = \mathcal {O} \RB {\chi}}, as claimed.

@@

We discuss the complexity of DS, Lasso, and OMP.
For DS, suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used \cite {BoV04}.
For our case, that would be \m {\mathcal {O} \SB {4 N_h ^2 \D 8 N_h} = \mathcal {O} \SB {N_h ^3}}.

### 2021-06-07 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
Copy the proof in chap 3 into article

\Result
{Theorem}
{
Suppose
%
\DispNum {N:R:sd'NH} {
N_R
\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_{H,t}
}
%
Then \m {\M {F}_R} (respectively \m {\M {W} _R}) has \m {\d_s} RIP for probability \m {p}, with
\DispNum {1:p:ex:d's} {
1 -p
\leq \RB {\frac {\d_s} {N_{H,t} s}} ^{1/3} 
}
}

@@

So, how do we relate RIP of \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} to RIP of \m {\M {P}}?
Notice
\DispNum {P:2:FB:WR} {
\VNm {P} _2
=\VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 
}
Since both \m {\M {F}_B^\intercal \M {F}_B^\Tr} and \m {\M {F}_B^\intercal \M {F}_B^\Tr} are \m {\d_s} RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s} RIP.
However, it is doubtful to assume that their Kronecker product still has RIP.

>>>>

\Result
{Proposition}
{
Suppose
%
\DispNum {N:R:sd'NH} {
N_R
\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_{H,t}
}
%
Then \m {\M {F}_R} (respectively \m {\M {W} _R}) has \m {\d_s} RIP for probability \m {p}, with
\DispNum {1:p:ex:d's} {
1 -p
\leq \RB {\frac {\d_s} {N_{H,t} s}} ^{1/3} 
}
}

@@

So, how do we relate RIP of \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} to RIP of \m {\M {P}}?
Notice
\DispNum {P:2:FB:WR} {
\VNm {P} _2
=\VNm {\M {F}_B^\Tr \M {F}_R^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 
}
Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {W}_B \M {W}_R} are \m {\d_s} RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s} RIP.
However, it is doubtful to assume that their Kronecker product still has RIP.
